First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-04 ms.tex
fixed units in diffuse model plot
Adding pointing cartoon figure
Starting text for ref pipe section

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{diffuse_sky.pdf}
\caption[Diffuse model used for subtraction]{
The diffuse foreground model within the EoR0 field used for foreground subtraction. This 
model was created using residual images from the golden data set. The image shown is 
smoothed to degree scales to emphasize the large scale structure and approximate an 
MWA snapshot natural weighting. The color scale is in units of Jy/degree$^2$.
\label{fig:diffuse}
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{jackknife.pdf}
\caption[Per pointing jackknife]{An example jackknife test. For this test we divided the data 
into days and pointings. This is an example array of power spectra (residual E-W 
polarization) for a single day, August 26, 2013. The early pointings are heavily contaminated 
by the galaxy in the sidelobes, the window becomes more clear near zenith, and we can 
see trace contamination at the end of the night (pointing +4) when the galaxy has risen 
again.
\label{fig:jackknife}
}
\end{center}
\end{figure*}

@@

\subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}
\textcolor{red}{Will inject comparison with RTS/CHIPS here.}
% ADAM: Motivation why a pipeline is being discussed
% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
% CATH: Plots
%     by pointing - diff zenith vs +2 
%	2D PS vs redshift
%	1D

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{diffuse_sky.pdf}
\caption[Diffuse model used for subtraction]{
The diffuse foreground model within the EoR0 field used for foreground subtraction. This 
model was created using residual images from the golden data set. The image shown is 
smoothed to degree scales to emphasize the large scale structure and approximate an 
MWA snapshot natural weighting. The color scale is in units of Jy/str.
\label{fig:diffuse}
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
%\subfigure{\includegraphics[width=\textwidth]{jackknife.pdf}}
\includegraphics[width=\textwidth]{jackknife.pdf}
%\subfigure{\includegraphics[width=.5\textwidth]{pointing_cartoon.pdf}}
\caption[Per pointing jackknife]{An example jackknife test. For this test we divided the data 
into days and pointings. This is an example array of power spectra (residual E-W 
polarization) for a single day, August 26, 2013. The early pointings are heavily contaminated 
by the galaxy in the sidelobes, the window becomes more clear near zenith, and we can 
see trace contamination at the end of the night (pointing +4) when the galaxy has risen 
again.
\label{fig:jackknife}
}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{pointing_cartoon.pdf}
\caption{\textcolor{red}{caption!}
\label{fig:pointing}
}
\end{center}
\end{figure}

@@

\subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}

As demonstrated in D.~C.~Jacobs et al. 2016 (in review), comparison between independent 
analysis pipelines is essential to evaluate the validity of algorithms under active development. 
Such comparison provides insight into the strengths and weaknesses of the pipelines, as well 
as confirmation of results. The analysis discussed so far has been based on the FHD to 
\eppsilon pipeline, and here we compare with the Real Time System \citep[RTS,][]
{Mitchell:2008,Ord:2010} to Cosmological \ion{H}{1} Power Spectrum \citep[CHIPS,][]
{Trott:2016} pipeline. Below we present a brief overview of the reference pipeline and 
highlight lessons learned from the comparison.

% ADAM: Motivation why a pipeline is being discussed
% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
% CATH: Plots
%     by pointing - diff zenith vs +2 
%	2D PS vs redshift
%	1D
